---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Homework6Package

<!-- badges: start -->
[| [R-CMD-check] (https://github.com/mj307/sparsevectors/actions/workflows/R-(MD-check.yaml/badge.svg)](https://github.com/mj307/sparsevectors/actions/workflows/R-CMD-Check.yamLS
<!-- badges: end -->

The goal of Homework6Package is to provide an efficient S4 class, sparse_numeric, for representing numeric vectors in sparse form. Only non-zero entries are stored, which can save memory and improve performance for large vectors. The package includes methods for:

- Arithmetic operations (+, -, *) on sparse vectors

- Computing mean, norm, and standardize

- Plotting non-zero entries for visual inspection

- Converting between dense (numeric) and sparse representations

## Installation

You can install the development version of Homework6Package like so:

```{r}
# install.packages("devtools") # if not already installed
devtools::install_github("0NancyYeung0/Homework6Package")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Homework6Package)

# Create a dense numeric vector

vec <- c(0, 5, 0, 0, 3, 0, 0, 1)

# Convert to sparse_numeric

sparse_vec <- as(vec, "sparse_numeric")
sparse_vec

# Compute mean

mean(sparse_vec)

# Compute norm

norm(sparse_vec)

# Standardize

standardize(sparse_vec)

# Plot non-zero values against another sparse vector

vec2 <- c(1, 0, 0, 2, 0, 0, 3, 0)
sparse_vec2 <- as(vec2, "sparse_numeric")
plot(sparse_vec, sparse_vec2)
```
